Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-02-12 Journal1/Response (21-10-2019)/Response.tex

%\documentclass[12pt, draftclsnofoot, onecolumn,letterpaper]{IEEEtran}
\documentclass[12pt, letterpaper]{article}
%\documentclass[12pt, letterpaper]{IEEEtran}
\usepackage{ multirow }
\usepackage{longtable}
\usepackage{geometry}
\usepackage{ragged2e}
\usepackage[table]{xcolor}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{lipsum}
\usepackage{makeidx}
\usepackage{enumerate}
\usepackage{color}
\usepackage{refstyle}
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{nomencl}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{anysize}
\usepackage{float}
\usepackage{epstopdf}
\usepackage{threeparttable}
\usepackage{multicol}
\usepackage{amssymb}
\usepackage{adjustbox}
%\usepackage[none]{hyphenat}
%\usepackage{float}

%\usepackage{fixltx2e}
\usepackage{amsmath, amssymb, upgreek, amsthm}
\usepackage{graphicx}
\usepackage{tikz}
\geometry{letterpaper, left=20mm, right=20mm, top=20mm, bottom=20mm}
\usetikzlibrary{patterns} % LATEX and plain TEX when using Tik Z
\allowdisplaybreaks
\setlength{\textfloatsep}{2ex}
\usepackage{array}
\usepackage{enumitem}
\setlength{\parindent}{1 em}
\setlength{\parskip}{0.5 em}
\renewcommand{\baselinestretch}{1.25}
\def\dsd{d_\text{SD}}
\def\Rcoop{R_\text{Coop}}
\def\rhd{R_\text{HD}}
\def\rsd{R_\text{SD}}
\def\rsh{R_\text{SH}}
\def\Pcoops{\mathcal{P}^\text{Succ}_\text{Coop}}
\def\dsh{d_\text{SH}}
\def\dhd{d_\text{HD}}
\def\psibar{\overline{\mathcal{P}}^\text{Succ}_{i}}
\def\psbara{\overline{\mathcal{P}}^\text{Succ}_{1}}
\def\psbarb{\overline{\mathcal{P}}^\text{Succ}_{2}}
\def\psbarc{\overline{\mathcal{P}}^\text{Succ}_{3}}
\def\psbard{\overline{\mathcal{P}}^\text{Succ}_{4}}
\def\psbare{\overline{\mathcal{P}}^\text{Succ}_{5}}
\def\Ri{R_{i}}
\def\Ps{\mathcal{P}^\text{Succ}_\text{Direct}}
\def\frk{\mathrm{f}_{r_k}(r)}
\def\Rcoopj{R_\text{coop}^j}
\title{\bf \vspace*{-4ex} Statement of Responses to the Editor and the Reviewers of Paper-TNSM \\[-6ex]}
\date{}

@@

\begin{document}
%\vspace*{-10ex}
%\sloppy
\maketitle
We would like to thank the editor and reviewers for their comments on our manuscript.
We hope that the modifications that we have made to the manuscript, and the responses that we have
provided herein will alleviate the reviewers' concerns. Below, please find our detailed responses to the editor and reviewers' comments and suggestions.
\\ [-3.ex]
% % % % % % % % % % % % % % % Editor % % % % % % % % % % % % % % % % % % % %

\clearpage
\noindent
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Editor} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comment1:} ``The paper has gone through three independent reviews and also checked by myself. The topic is interesting and there are merits. But there are some major concerns on the contribution, the assumption, the model derivation, and the experimental results. I hope the review comments are useful for further improving the quality of the paper. I'd therefore recommend the Resubmission''\\
\hline
\end{longtable}

\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the editor for his comment on our manuscript and giving us the opportunity to resubmit it. We have utilized the comments to improve our paper and eliminate the problems.

%\begin{longtable}{|p{0.975\textwidth}|}
%\hline \hline
%\RaggedRight
%\cellcolor{green!10}
%[1] F. Patolsky, B. P. Timko, G. Yu, Y. Fang, A. B. Greytak, G. Zheng, and C. M. Lieber, ``Detection, stimulation, and inhibition of neuronal signals with high-density nanowire transistor arrays,'' Science, vol. 313, no. 5790, pp. 1100-1104, 2006.
%\\
%\hline
%\end{longtable}

% % % % % % % % % % % % % % % Reviewer 1 % % % % % % % % % % % % % % % % % % % %
\clearpage
\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 1} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{violet!15}
\textbf{\noindent Comments to the Author} ``
The paper proposes resolving the problem of resource allocation to network slices by using a new algorithm applied to the reformulation of the problem. The results seem promising but the paper has some issues. ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We would like to thank the reviewer for the careful and thorough reading of this manuscript. We hope that the responses provided herein can alleviate the reviewer's concerns.

\noindent
\begin{longtable}{|p{.975\textwidth}|}
\hline \hline %\hline \hline \hline
\Centering
\cellcolor{gray!60}
\textbf{Reviewer 1} \\
\hline \hline %\hline \hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``First, the structure of the paper makes it somewhat hard to follow and there are some mistakes in the text. A proofread is required before it can be accepted for publication.   ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
I have changed the paper's introduction and checked the text entirely according to this comment.

### 2022-02-12 Journal1/paper3TNSM/pr.tex
finish question and start write on latex

Recent discussion of 5G wireless systems has been around three services, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC). Depending on QoS, each service requires its own slice of the network.
The eMBB service fulfills the demand for high capacity and throughput. The URLLC also offers autonomous vehicles, tactile internet, remote surgery services, and other services of high quality and low latency. mMTC is comprised of many low-power internet of things (IoT) devices that transmit small payloads to a typical receiver, including sensors for sensing, metering, and monitoring

@@

\textcolor{OrangeRed}{This paper considers various user equipments (UEs) requesting one of these types of services with different QoS. We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.}

\textcolor{blue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks. O-RAN was developed as a result of integrating virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both. With RAN virtualization, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to the network more quickly. The CRAN divides the radio remote head (RRH) and baseband unit (BBU) into two major parts. Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}. Unlike CRAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).}

O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node with higher PHY, MAC, and RLC.
In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud. 
O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence 
\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.

@@

\textcolor{blue}{In order to achieve the specific QoS for eMBB, URLLC, and mMTC, this study optimizes the allocation of baseband resources, including power allocation, PRB allocation, O-Rus association, and VNF activation to create an isolated network slicing outline.}
\subsection{Related Literature}
The problem of resource allocation for network slicing in multi-tenant cellular networks has received attention recently \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in multi-tenant heterogeneous CRAN (H-CRAN) is considered. The network slicing scheme includes a higher level and the lower level. The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity. Also, the allocation of power and physical resource blocks (PRB) is performed in the lower level.
In \cite{xiang2020realization}, network slicing in the radio section is considered for the fog RAN (F-RAN) system, and a deep reinforcement learning algorithm is proposed for it. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed in mobile network operator (MNO).

@@

In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also the problem of RRH to BBU and the RRH to UE association is obtained. Moreover, the author talked about the feasible region to make the initial values possible.
\subsection{Main Contributions}
The purpose of this study is to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform.
Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN system.
The novelty of this paper is to improve the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing.
In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follows:
\item This paper depicts a network slicing model for three different services introduced in 5G, i.e., eMBB, mMTC, and URLLC. The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for different types of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different types of services. We formulate the end-to-end processing delay of the system based on the number of activated VNFs and user throughput.
Assuming a limited fronthaul capacity, we calculate the power and capacity of each O-RU. We model the interference of neighboring O-RUs and formulate the actual throughput for different service types. Based on the short packet transmission of URLLC and mMTC, we also model their throughput.
\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
\begin{figure*}
    \includegraphics[scale = 0.45]{finalDraw.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
The rest of this paper is organized as follows. The system model and the problem formulation are described in Section \ref{systemmodel}. The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Section \ref{conc} concludes the  paper.
\section{System Model and Problem Formulation}\label{systemmodel}
In this section, we describe the downlink system in O-RAN using RAN slicing as depicted in Figure \ref{fig:c11}. 
Firstly, we present the system model. Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the ORAN system. Afterward, we discuss the mean delay and the power of VNFs.
Finally, the main problem is expressed.
\subsection{System Model}
There are three service types including eMBB, URLLC, and mMTC which support different applications. There are $S_1$, $S_2$ and $S_3$ different applications for the eMBB, URLLC, and mMTC service types, respectively and we have $S = S_1 + S_2 + S_3$. 
%{\color{red} explain pre-allocated more}
Therefore, there are $S$ pre-allocated slices serving these $S$ services;
Each pre-allocated slice contains reserved VNFs for the three logical nodes:
\item The MAC/RLC functions in the O-DU logical node
\item The PDCP/SDAP functions in the O-CU-UP logical node
\item The UPF logical node

@@

\textcolor{Sepia}{Interference occurs when a UE in O-RU $r$ using PRB $k$ experiences an interference signal from other O-RUs in the set of $r' \in R \not\in
 r$. UEs in each slice interfere in two ways in the technique of network slicing: the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.
Network Slicing methods significantly reduce inter-service interference.
There are some techniques to remove inter-slice interference. One of these techniques is to have two-time scale scheduling. The PRB scheduling to the slices is performed on the first time scale, and in the second time scale, the PRB scheduling to the UEs of slices is carried out. Since there are limited resources, inter-service interference cannot be eliminated entirely. The other method is to allocate part of the RB of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.} In this paper, we assume that the PRB scheduling is performed. Also, in subsection \ref{prb}, we briefly study the PRB scheduling between slices.
\begin{figure}
  \centering 
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.40]{Interference.png}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Type of Interference Signal}
  \label{fig:intf}
\end{figure}
\textcolor{teal}{ $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow}
%{\color{red} use paranthesis in the following equation to clear +}
\begin{subequations}\label{eqI}
\begin{alignat}{4}
&I_{r,u(s,i)}^{k} =\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{alignat}
\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)
\textcolor{Sepia}{Furthermore, there is no inter-slice interference since slices are isolated and there is just intra-slice interference.}

@@

\textcolor{RedViolet}{In this subsection, we want to study the management of slices. We want to talk about the creation, management, and deletion of slices.}

@@

\vspace*{-2em}

@@

>>>>

Recent discussion of 5G wireless systems has been around three services, namely enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC), and massive machine-to-machine communications (mMTC). Depending on QoS, each service requires its slice of the network.
The eMBB service fulfills the demand for high capacity and throughput. The URLLC also offers autonomous vehicles, tactile internet, remote surgery services, and other services of high quality and low latency. mMTC comprises many low-power internet of things (IoT) devices that transmit small payloads to a typical receiver, including sensors for sensing, metering, and monitoring

@@

\textcolor{blue}{This paper considers various user equipments (UEs) requesting one of these types of services with different QoS. We want to study RAN slicing technology and the isolation between slices in this system to evaluate the performance of various services.}

\textcolor{blue}{O-RAN is driven by two pillars of openness and RAN intelligence as the next generation of radio access networks. O-RAN was developed due to integrating virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both. With RAN virtualization, operators can improve flexibility, reduce CAPEX and OPEX, and add new capabilities to the network more quickly. The CRAN divides the radio remote head (RRH) and baseband unit (BBU) into two major parts. Several distributed RRHs can be connected to a centralized BBU, called BBU-pool \cite{han2019research}. Unlike CRAN, O-RAN separates RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).}

\textcolor{blue}{O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node with higher PHY, MAC, and RLC.
In addition, the O-CU contains two parts: the O-CU user plane (O-CU-UP) and the O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation, RAN Intelligent Controller (RIC)- Near Real-Time, and O-Cloud\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.}

\textcolor{blue}{This paper aims to design a RAN slicing technology in O-RAN architecture. }
%O-RAN offers machine learning techniques based on the requirement for an intelligent wireless network for the next generation of RAN systems. The two logical nodes, RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC-Near Real-Time, implement the algorithms for network intelligence

@@

\textcolor{blue}{This study presents a technique for creating isolated network slices outlines in O-RAN architecture to provide the specific QoS for eMBB, URLLC, and mMTC. As well as baseband resources, the optimal number of VNFs is also taken into account to reduce latency for URLLC services.}
\subsection{Related Literature}
The problem of resource allocation for network slicing in multi-tenant cellular networks has received attention recently \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in multi-tenant heterogeneous CRAN (H-CRAN) is considered. The network slicing scheme includes a higher level and the lower level. The higher level manages user acceptance control, user communication that provides for radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity. Also, the allocation of power and physical resource blocks (PRB) is performed in the lower level.
In \cite{xiang2020realization}, network slicing in the radio section is considered for the fog RAN (F-RAN) system, and a deep reinforcement learning algorithm is proposed for it. In \cite{elayoubi20195g,d2020toward}, the implementation of RAN level slicing is discussed in mobile network operator (MNO).

@@

In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also the problem of RRH to BBU and the RRH to UE association is obtained. Moreover, the author talked about the feasible region to make the initial values possible.
\subsection{Main Contributions}
\textcolor{MidnightBlue}{The purposes of this paper are twofold. First and foremost, our goal is to design a system in the O-RAN structure with three types of services, namely, eMBB, URLLC, and mMTC. Simultaneously, it maximizes the total achievable data rate and meets the conditions of URLLC service low latency in the presence of numerous IoT devices requiring low power, leading to RAN slicing. Second, to model the delay for URLLC systems, we deal with the problem of obtaining the optimal number of VNFs in different layers of the O-RAN system. 
In this paper, we want to optimize baseband resource allocation, i.e., power allocation, PRB allocation, O-RUs association, and VNF activation, to develop an isolated network slicing outline for different types of services in an O-RAN platform. 
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms to achieve these purposes.
Unlike other papers, we concentrate more on the multiservice resource management of the RAN slicing in the openness and flexible O-RAN architecture.
The novelty of this paper is to enhance the resource utilization of the overall wireless O-RAN system in the presence of the three generic service types introduced in 5G using RAN slicing. We also convexify and solve complex problems using mathematical concepts and obtain optimal resources.}

In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the o-ran system is studied. The main contributions of this paper are summarized as follows:
\begin{itemize}
\item This paper depicts a network slicing model for three different services introduced in 5G, i.e., eMBB, mMTC, and URLLC. The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for different types of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different types of services. We formulate the end-to-end processing delay of the system based on the number of activated VNFs and user throughput.
Assuming a limited fronthaul capacity, we calculate the power and capacity of each O-RU. We model the interference of neighboring O-RUs and formulate the actual throughput for different service types. Based on the short packet transmission of URLLC and mMTC, we also model their throughput.
\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\item We talk about the initial point and the feasible region for the numerical results and introduce a fast algorithm that is less complex than our method to realize the feasible region for our problem.
\end{itemize}  
\begin{figure*}
  \centering 
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.45]{finalDraw.pdf}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced o-ran system}
  \label{fig:c11}
\end{figure*}
The rest of this paper is organized as follows. The system model and the problem formulation are described in Section \ref{systemmodel}. The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Section \ref{conc} concludes the  paper.
\section{System Model and Problem Formulation}\label{systemmodel}
In this section, we describe the downlink system in O-RAN using RAN slicing as depicted in Figure \ref{fig:c11}. 
Firstly, we present the system model. Then, we obtain achievable data rates, power of O-RU, and the fronthaul capacity for the downlink (DL) of the o-ran system. Afterward, we discuss the mean delay and the power of VNFs.
Finally, the main problem is expressed.
\subsection{System Model}
There are three service types including eMBB, URLLC, and mMTC which support different applications. There are $S_1$, $S_2$ and $S_3$ different applications for the eMBB, URLLC, and mMTC service types, respectively and we have $S = S_1 + S_2 + S_3$. 
%{\color{red} explain pre-allocated more}
Therefore, there are $S$ pre-allocated slices serving these $S$ services;
Each pre-allocated slice contains reserved VNFs for the three logical nodes:
\begin{itemize}
\item The MAC/RLC functions in the O-DU logical node
\item The PDCP/SDAP functions in the O-CU-UP logical node
\item The UPF logical node
\end{itemize}

@@

\textcolor{Sepia}{Interference occurs when a UE in O-RU $r$ using PRB $k$ experiences an interference signal from other O-RUs in the set of $r' \in R \not\in
 r$. UEs in each slice interfere in two ways in the technique of network slicing: the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in figure \ref{fig:intf}.
Network Slicing methods significantly reduce inter-service interference.
There are some techniques to remove inter-slice interference. One of these techniques is to have two-time scale scheduling. The PRB scheduling to the slices is performed on the first time scale, and in the second time scale, the PRB scheduling to the UEs of slices is carried out. Since there are limited resources, inter-service interference cannot be eliminated entirely. The other method is to allocate part of the RB of eMBB services to URLLC and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}.} In this paper, we assume that the PRB scheduling is performed. Also, in subsection \ref{prb}, we briefly study the PRB scheduling between slices.
\begin{figure}
  \centering 
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.35]{Interference.png}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Type of Interference Signal}
  \label{fig:intf}
\end{figure}
\textcolor{teal}{ $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as follow}
%{\color{red} use paranthesis in the following equation to clear +}
\begin{subequations}\label{eqI}
\begin{alignat}{4}
&I_{r,u(s,i)}^{k} =\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{alignat}
\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)
\textcolor{Sepia}{Furthermore, there is no inter-slice interference since slices are isolated and there is just intra-slice interference.}

@@

\textcolor{RedViolet}{This subsection aims to examine slice management, including creating, managing, and deleting slices. Network slices generally have four life cycle stages: preparation, commissioning, operation, and decommissioning. 
\item Preparation phase: The network slice instance (NSI) does not exist in the preparation phase. In this phase, operators plan to create an NSI, such as designing the NSI template, onboarding users, and preparing the environment. Also, the evaluation of requirements is performed in this step.
\item Commissioning phase: In the commissioning phase, the creation of the NSI is done. In this phase, the requirements are considered and allocated to the slice. 
\item Operation phase: During the Operation phase, NSIs are activated, managed, monitored (e.g., KPIs), modified, and deactivated. As the slice enters the activated phase, it is ready to support services, and as the slice exits the de-activated phase, the slice is inactive, and communication services are stopped.
\item Decommissioning phase: A NSI that is decommissioned no longer exists after the decommissioning phase.

@@

%\vspace*{-2em}

@@

%\vspace*{-1.7em}
